Project Review Template

### 2025-04-26 project-review-Gonzalez.qmd

---
title: Project Review Template 
author: Murphy John
date: date-modified
format: 
  html:
    toc: true
    toc-depth: 3
    number-sections: true
---

@@

Name of project reviewer: Murphy John

@@

- Add references in your intro
- Elaborate on the importance or motivation for your research question. Is there any prior evidence of an association? Why is this an important topic to explore?
- Why are you restricting the age to under 50? It looks like you have data for other ages. If you want to emphasis that this study is looking in young adults then include more background on CVD prevalence in young adults. Maybe there are different risk factors in this age group compared to older individuals? That could provide more motivation for your research question.

### Summary assessment
* some contextualization and motivation

@@

- Line 17, say "individuals under 50 years of age" or something to clarify the age range.
- What do you hypothesize? Why do you think that?

### Summary assessment
* question/hypotheses somewhat explained

@@

- Line 25, just say "the primary outcome is presence or absence of heart disease". I'm not sure what the word target means in this sentence.
- Add a reference to line 23 "These thresholds were chosen based on clinical relevance".
- Talk more about the data source. Where did it come from (what specific hospital)? When was it collected? Who was included in the data collection? What was the inclusion/exclusion criteria for this study? 
- BMI, family history, SES, and smoking status are confounders of CVD. If you have data on these, include it. If not, this needs to be discussed in the limitations.
- Your study population needs to be more specific. Is it adults worldwide? In India? In a specific area of India?
- What is oldpeak?
- After the inclusion/exclusion critera, how many individuals/obervation are in your data?

### Summary assessment
* source and overall structure of data somewhat explained

@@

- You need to load your processed data at the start of each script. None of your scripts are running because of this. To make sure everything works and is reproducible, clear your environment before you run anything in a new script.
- The data processing looks good so far but you should include your inclusion/exclusion criteria in that script (ie filter age < 50). 
- Your eda should be of the data used in your analysis (ie age < 50). This will likely change your findings and perhaps your analysis decisions.
- Your plots look nice.

### Summary assessment
* some weaknesses in wrangling and exploratory component

@@

- You have processing code in your analysis-code/01_inferential_stats.qmd file. This should be in the processing code file. You also have eda in this file that should go in the eda folder.

In analysis-code/02_modeling.qmd:

- Why are you fitting linear models to a binary variable?
- Use logistic regression instead of linear.
- If you want to use lasso, use logistic_reg() in your spec.
- For your random forest model, set mode to "Classification" instead of regression.
- RMSE is for continuous outcomes, use AUC and/or accuracy for your metrics instead.
- Use test/train data split and/or cross-validation for model selection.

analysis-code/03_model_tuning.qmd:

- You need to load your model objects from the previous scripts or merge this script with the previous one.
- It doesn't make sense to use rmse for metrics
- You need to use binary outcome modeling methods in the modeling script then update this script (or merge the two)

### Summary assessment
* wrong/inadequate analysis

@@

- The descriptive statistics table should be of the data you analyze (age < 50).
- The tables and figures need to render to the manuscript doc

### Summary assessment
* results are presented ok, with room for improvement

@@

- For the current analysis set up, the discussion is set up well. Once you implement the correct analysis methods you'll likely get different results.
- Your limitations sections needs to address the confounders that you don't control for. Also if there are any data collection limitations list that here.

@@

@@

- Project structure looks good.
- Your analysis code contains some data processing and eda that should be in different locations.

### Summary assessment
* well structured

@@

- looks good

### Summary assessment
* fully and well documented

@@

- Your manuscript wouldn't render as is. You need to fix your figures and tables code.
- None of your eda or analysis scripts run because you haven't loaded the data in them. Use cardio_df <- readRDS(here::here("data/processed-data/cleaned_df.rds"))
- Project is not reproducible- you need to load data and model objects in each script.

### Summary assessment
* small parts not reproducible or required manual intervention

@@

Given the data presented, the project analysis is thorough. It isn't correct in the current methods but with minor edits, you should get more appropriate results. My biggest concerns are the eda on the unused data, the incorrect modeling methods, and the lack of control for major CVD confounders.

### Summary assessment
* strong level of thoroughness

@@

- References are not properly loaded. Consider using .bib file. Zotero is a nice software for storing references and generating .bib files.

>>>>

---
title: Project Review Template 
author: YOUR NAME
date: date-modified
format: 
  html:
    toc: true
    toc-depth: 3
    number-sections: true
---

@@

Name of project reviewer: Alexis Gonzalez

@@

The introduction needs contexualization. Why is this issue important? What is the current scope? Maybe provide some global statistics and some India specific statistics.

### Summary Assessment

* some contextualization and motivation

@@

Question is clear, I understand your goal.

### Summary assessment
* question/hypotheses unclear

@@

I do not really understand the dataset. How was this data obtained, where is this hospital specifically? Might be good to include some parts of the dataset description from the website you got it from.

### Summary assessment

* source and overall structure of data somewhat explained

@@

Unfortunately, I am unable to load the data in your manuscript. I still want to give feedback so I will look at your code file.

- Instead of the basic table output consider using flextable for KableExtra
- It doesn't look like you include any of your figures from EDA. Those are actually very helpful for getting an idea of distributions and burden.
- The EDA should help explain the formulation of your question or provide some reason why.
- The code is very very neat and the graphs look great!!

### Summary assessment

* some weaknesses in wrangling and exploratory component

@@

I do not think you need the linear model here for a binary outcome, the log model makes more sense.

### Summary assessment

* defensible but not optimal analysis

@@

I like how the results section is sectioned out, makes it easy to follow. Figures look nice.

### Summary assessment

* results are very well presented

@@

The discussion is lacking in explanation of the results.

@@

_Add any other comments regarding the different aspects of the project here. Write anything you think can help your classmate improve their project._

@@

Porject is structured well, easy to follow

### Summary assessment

* well structured

@@

Code is well documented and easy to follow

### Summary assessment

* fully and well documented

@@

The manuscript needs to be fixed and I was unable to run the cross validation for your RF model

### Summary assessment

* small parts not reproducible or required manual intervention

@@

Overall I would say the study was thorough. I think you should go back and expand on your introduction, discussion and conclusion. Explain the reason for using LASSO and RF. Also make sure to add some EDA plots into your manuscript.

### Summary assessment

* decent level of thorougness

@@

don't forget to properly format references! This is a great study I can't wait to read the final product.
